ESRC SDAI Application

### 2019-06-24 case_for_support.tex
Anna update

As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature. Estimates show that on average, victims live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}. The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey including a self-completion module on domestic abuse. According to the CSEW, of those respondents who experienced domestic abuse between April 2017 and March 2018, only 17\% reported it to the police \cite{ONS}. This extremely high level of underreporting is another characteristic that is specific to domestic abuse.

@@

Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020. The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.

@@

The two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights. The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (victim). However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators and has limited longitudinal information. In contrast, the crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships and identify the predictors of escalation. Information on the exact timing of the abuse and the time of reporting will help us identify high-risk times of the year and understand the factors influencing the decision to report. Information on alcohol involvement is more likely to be accurate in the crime dataset than in the self-completion survey. Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender and victim.  We do not intend to link the two datasets.

@@

\subsection*{1. Understanding domestic abuse: victim characteristics, extent of domestic abuse and police mis-recording}

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In our first research project, we will be investigating three main research questions. First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data. Second, we will estimate the true extent of domestic abuse victimisation. Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the extent of domestic abuse victimisation and the subsequent societal costs. We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related). Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide. Finally, we will estimate the extent of police mis-recording of domestic abuse. Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm. By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.

@@

\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors predicting domestic abuse victimisation. Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse ever suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use. Using this wide range of individual-level information, we will evaluate the importance of each of these variables in predicting the likelihood of domestic abuse victimisation. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance? this way we could also look at interactions? does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW. We are particularly interested in the association between experiences of domestic abuse, number of children and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.

Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the victim reported the domestic abuse to the police. The WMP contains information about the sex and age of victims. We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW \textit{(we were initially talking about using victims of burglary, but maybe this is better?)}. We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.

@@

\textbf{Aim 2.}  While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a victim of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons. First, because it does not collect detailed information on repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases), but only on the number of incidents involving physical violence perpetrated by household members. In addition, victims who suffer frequent, ongoing abuse are less likely to accurately remember the exact number of incidents. Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, financial abuse, burglary). In addition, it does not collect information on whether different offences against the same victim were perpetrated by the same offender. In contrast, the WMP data allows us to tell if a reported case was domestic abuse related, regardless of the actual offence committed. In addition, it allows us to identify various incidents where the same victim-offender pair were involved. We can estimate the co-morbidity of self-reported victimisation by crime type using the CSEW. We can contrast this with the estimated co-morbidity of reported victimisation from the police data. \textit{is this silly? then we can maybe estimate what percentage of true victimisation is domestic-abuse related? the £66 billion cost estimate is based on the CSEW}

%It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes. It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes. We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse. The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.

\textbf{Aim 3.} Police forces in England, including the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents. By contrasting the extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP. Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time. We can complement this investigation with analysing the self-reported outcome of incidents that have been reported to the police from the CSEW.

@@

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}

@@

\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} escalation often happens when the abuser feels like they are losing control (e.g., because the victim threatens to leave); separation is an important risk factors of serious harm;

@@

@@

does the level of harm depend on the length of time spent in the relationship, separation,

Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.

\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the victim (especially focusing on the issue of separation and divorce, as evidence suggests it is a significant risk factor predicting serious harm). We will also explore whether non domestic abuse-related victimisation is predictive of serious harm. We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.

Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.

@@

%We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours. Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk. In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes. It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.

\textbf{Aim 2.} First, we will use the CSEW, and a logistic approach to understand how the decision to report to the police (or seeking any external help) depends on the individual-level characteristics of the victim (especially focusing on mental and physical health, financial independence and whether the victim has children) and the abuse suffered. We can complement this analysis with the WMP data,

children's safety as a concern

Second, using the WMP data, we will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

@@

%Regression 4: offense classification[proxy for harm] ~ .
%	type of abuse ~ .
%
%Future victim behaviours. Future perpetrator behaviours
%
%serious event at t ~ stuff at t-1  + perpetrator previous crimes
% and 	a model with pair fixed effects
%
%Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents. 
%
%Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.

@@

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
Domestic abuse has long-lasting adverse effects on victims and those close to them. In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household. Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design victim support programmes and quantify the societal harm caused by it.

@@

Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a victim of a domestic abuse offender. No control group.

@@

%Aim:
%
%CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
%Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below
%
%It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
% 
% explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems? No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse? Following people over time (Dynamic topic modelling for victims)- what’s the temporal order? 
%
%Match on name, location, and date of birth in WMP data to see effect on children
%
%WMP regression:
%
%take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse
%
%What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse
%
%Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.

>>>>

As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature. Estimates show that on average, survivors live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}. The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey including a self-completion module on domestic abuse. According to the CSEW, of those respondents who experienced domestic abuse between April 2017 and March 2018, only 17\% reported it to the police \cite{ONS}. This extremely high level of underreporting is another characteristic that is specific to domestic abuse.

@@

%Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020. The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase survivor safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.

@@

The two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights. The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor). However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators and has limited longitudinal information. In contrast, the crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships and identify the predictors of escalation. Information on the exact timing of the abuse and the time of reporting will help us identify high-risk times of the year and understand the factors influencing the decision to report. Information on alcohol involvement is more likely to be accurate in the crime dataset than in the self-completion survey. Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender and victim. We do not intend to link the two datasets.

@@

\subsection*{1. Understanding domestic abuse: survivor characteristics, extent of domestic abuse and police mis-recording}

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In our first research project, we will be investigating three main research questions. First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data. Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.

Second, we will estimate the true extent of domestic abuse victimisation. Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the prevalence of domestic abuse. We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related). Estimating the true prevalence of domestic abuse across various types of criminal offences will help us to obtain a better estimate of the societal cost associated with domestic abuse.

%Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide.

Finally, we will estimate the extent of police mis-recording of domestic abuse. Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm. By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.

@@

\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors predicting domestic abuse victimisation. Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse ever suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use. Using this wide range of individual-level information, we will evaluate the importance of each of these variables in predicting the likelihood of domestic abuse victimisation. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance? this way we could also look at interactions? does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW. We are particularly interested in the association between experiences of domestic abuse, number of children, and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.

Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police. The WMP contains information about the sex and age of victims. We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW \textit{(we were initially talking about using victims of burglary, but maybe this is better?)}. We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW, which distinguishes between family and intimate partner violence.

@@

\textbf{Aim 2.}  The CSEW is used to estimate the costs of domestic abuse in the UK. While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a survivor of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons. First, because it does not collect detailed information on various aspects of repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases), as it only records the number of incidents involving physical violence perpetrated by household members (and ignores repeated cases of non-physical violence). In addition, survivors who suffer frequent, ongoing abuse are less likely to accurately remember the exact number of incidents. Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, financial abuse, burglary). In addition, it does not collect information on whether different offences against the same survivor were perpetrated by the same offender. In contrast, the WMP data allows us to tell if a reported case was domestic abuse related (as the police is required to record this information), regardless of the actual offence committed. In addition, it allows us to identify various incidents with the same victim-offender pair, providing us with reliable data on reported cases of repeat victimisation. We can estimate the co-morbidity of domestic abuse victimisation with other types of criminal victimisation using the CSEW. We can combine this with the estimated likelihood of domestic abuse victimisation by offence type to get a better estimate of the overall extent of domestic abuse victimisation (reported and unreported). \textit{is this silly? then we can maybe estimate what percentage of true victimisation is domestic-abuse related? the £66 billion cost estimate is based on the CSEW}

%It is common that individuals are more likely to be a survivor of crime if they have previously been a survivor of crime, and if they have perpetrated crimes. It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the survivor of crimes. We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse. The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.

\textbf{Aim 3.} Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents. By contrasting extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the recorded number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP. Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time. We can complement this investigation with analysing the self-reported outcome of incidents that have been reported to the police from the CSEW, and the survivor's perception of the CJS.

@@

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we are interested in exploring the risk factors of serious harm and the factors determining the decision to report the abuse. First,...
 Second,...
 does the level of harm depend on the length of time spent in the relationship, separation,

Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
 Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

@@

\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} often happens when the abuser feels like they are losing control (e.g., because the survivor threatens to leave); separation is an important risk factors of serious harm; contact over children

@@

decision to report: serious violence; friends, family, neighbours notice; happens in public, in front of people

@@

\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the survivor. We are especially interested in the co-morbidity of separation and divorce wand serious physical harm, as evidence suggests that the survivor's decision to end the relationship is a significant risk factor predicting serious harm. We will also explore whether non domestic abuse-related victimisation is predictive of serious harm. We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.

%Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.

Second, we will use the WMP

@@

%We can examine whether a recorded survivor of domestic abuse was previously recorded as a survivor in other crimes, and if they were subsequently a survivor of other criminal behaviours. Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk. In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes. It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.

Serious harm can be the cause or the consequence of the decision to report.

\textbf{Aim 2.} First, we will use the CSEW, and a logistic regression approach to understand how the decision to report to the police (or the decision to seek any form of external help) depends on the individual-level characteristics of the survivor (especially focusing on mental and physical health, financial independence and whether the survivor has children), and the severity and type of the abuse suffered. We are also interested in the link between the decision to report and survivor's general trust in the CJS.

Second, we can use the WMP data to investigate drivers of the decision to report. For this analysis, we will focus on the subset of incidents (6\% of all incidents), where the victim reported a long history of abuse (at least 3 days between first and last reported occurrence). We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, Halloween, Easter, etc.), potentially reflecting cases where the abuse has suddenly escalated, or became known to outsiders.

@@

%Regression 4: offense classification[proxy for harm] ~ .
%	type of abuse ~ .
%
%Future survivor behaviours. Future perpetrator behaviours
%
%serious event at t ~ stuff at t-1  + perpetrator previous crimes
% and 	a model with pair fixed effects
%
%Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents. 
%
%Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.

@@

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
Domestic abuse has long-lasting adverse effects on victims and those close to them. In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household. Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.

@@

Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a survivor of a domestic abuse offender. No control group.

@@

%Aim:
%
%CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
%Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below
%
%It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a survivor of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
% 
% explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems? No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse? Following people over time (Dynamic topic modelling for victims)- what’s the temporal order? 
%
%Match on name, location, and date of birth in WMP data to see effect on children
%
%WMP regression:
%
%take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse
%
%What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse
%
%Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.
